Attempting to write a full model

### 2016-09-14 R/misc/fullModel.rmd
test

>>>>

full_model_rcpp <- function(t, yini, parameters){
	return(list(unlist(g2(t, yini, parameters))))
}

pp <- expand(HIVpars.mean)

tvec <- seq(1, 30, 0.5)

r_rcpp <- lsoda(unlist(yini2), func = full_model_rcpp, parms = pp, times = tvec)
N_rcpp <- with(expand(HIVpars.mean),{
        S <- r_rcpp[,2:(1+n.risk)]
        I <- apply(r_rcpp[,(2+n.risk):(1+n.risk+n.risk*n.alpha)], 1, function(x) colSums2(x, n.alpha))
        return(S + t(I))
})

r_full <- lsoda(unlist(yini2), func = model2(HIVpars.mean, infection = TRUE, mortality = TRUE), parms = HIVpars.mean, times = tvec)
N_R <- with(expand(HIVpars.mean),{
        S <- r_full[,2:(1+n.risk)]
        I <- apply(r_full[,(2+n.risk):(1+n.risk+n.risk*n.alpha)], 1, function(x) colSums2(x, n.alpha))
        return(S + t(I))
})

all.equal(N_rcpp, N_R)

library(microbenchmark)
microbenchmark(
	rcpp = lsoda(unlist(yini2), func = full_model_rcpp, parms = pp, times = tvec),
	R= lsoda(unlist(yini2), func = model2(HIVpars.mean, infection = TRUE, mortality = TRUE), parms = HIVpars.mean, times = tvec)
)

Junk:

```{r junk, eval = FALSE}
